Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
Skype meeting

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
 \\
\text{and\qquad }
 \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p  
		\end{mathpar} 
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

Also note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{n_2 l} = s'_l$.

%In this case, the number of weak open transitions
%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
Note that \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = 
\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
We now have (the $\alpha'_p$ correspond to the observable $\alpha_k$ actions): \TODO{add ref to eq 1 page above?}
\begin{eqnarray*}
\Pred_\beta &\iff& \gamma_{j_0}=
\mybigdotcup_{p=0}^{p=n_1+n_2+2}
\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
%&\iff&\gamma_{j_0}=
%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
%&\iff& \gamma_{j_0}=
%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
&\iff& \gamma_{j_0}=
[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
\end{eqnarray*}

@@

And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta')_{3pj}^{j\in J\cap \Holes(Q)}$ (re-indexed), and additionally $(\beta')_{1pj}^{j\in J\cap \Holes(Q)}$, $(\beta')_{2j}^{j\in J\cap \Holes(Q)}$, and $(\beta')_{3pj}^{j\in J\cap \Holes(Q)}$ are identical to the holes labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta')_{1pj}^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes perform no action}. We can assert a similar equality on postconditions, i.e. between $\Post''_p$ and $\Post''_{1k}$, $\Post''_{2}$, $\Post''_{3k}$ where $\Post''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above). Overall, we have
{\scriptsize \begin{equation*}
\begin{split}
\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta')_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}\right)\\
&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
\end{split}\end{equation*}
}
\[\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i \text{see above}\]

@@

&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right ) \\
		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\

@@

$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land \Pred_2\bigotimes_{h=k}^{0}\subst{\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\big(\bigotimes_{j=h-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{h=k}^{0}\subst{\Post_{1h}}\big)
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\subst{\Post_2}\bigotimes_{j=k}^{0}\subst{\Post_{1j}}
$

@@

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
\begin{equation*}
\begin{split}
\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
(\alpha'_Q=\beta_{j_0})subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\Post_c&=\Post\uplus\Post_Q
\end{split}
\end{equation*}
\qed
\end{proof}

@@

Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction
\[P[Q]_{j_0} \models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
\]
and thus we also have a weak OT by definition:
\[P[Q]_{j_0} \models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTWeakarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
\]
\item idem for the OT $\alpha$
\item idem for the last $]\tau$s
\end{enumerate}

>>>>

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
 \\
\text{and\qquad }
 \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} )
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p  
		\end{mathpar} 
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.

By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$

%In this case, the number of weak open transitions
%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
Consequently \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = 
\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
We now have (the $\alpha'_p$ correspond to the observable $\alpha_k$ actions): \TODO{add ref to eq 1 page above?}
\begin{eqnarray*}
\Pred_\beta &\iff& \gamma_{j_0}=
\mybigdotcup_{p=0}^{p=n_1+n_2+2}
\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
%&\iff&\gamma_{j_0}=
%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
%&\iff& \gamma_{j_0}=
%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
&\iff& \gamma_{j_0}=
[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
\end{eqnarray*}

@@

And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}. We can assert a similar equality on postconditions, i.e. between $\Post''_p$ and $\Post''_{1k}$, $\Post''_{2}$, $\Post''_{3k}$ where $\Post''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above). Overall, we have
{\scriptsize \begin{equation*}
\begin{split}
\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
\end{split}\end{equation*}
}
\[\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i \text{see above}\]

@@

&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\

@@

$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
$

@@

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
\begin{equation*}
\begin{split}
\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\Post_c&=\Post\uplus\Post_Q
\end{split}
\end{equation*}
\qed
\end{proof}

@@

Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction
\[P[Q]_{j_0} \models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
\]
and thus we also have a weak OT by definition:
\[P[Q]_{j_0} \models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTWeakarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
\]
\item idem for the OT $\alpha$
\item idem for the last $\tau$s
\end{enumerate}
